\vspace{5cm} \normalsize \textsc{\NetIDb} \\ [2.0cm] \HRule{0.5pt} \\ \LARGE \textbf{\uppercase{\documenttitle}} \HRule{2pt} \\ [0.5cm] \normalsize \textsc{Sergio Castañeiras Morales\\NIU:1598456\\ }\normalsize \vspace*{5\baselineskip}

### 2025-06-02 Manuscript/Plantilla memòria TFG 2024_25.tex
Stuff

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
%----------FONT AND GEOMETRY DEFINITION----------%
\usepackage[a4paper, hmargin=3.0cm, vmargin=3.0cm]{geometry}
\voffset = -0.75cm
\usepackage{arev}
\usepackage{helvet}
\renewcommand{\rmdefault}{\sfdefault}
\usepackage[math]{blindtext}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd, esint}
%---------SPACING----------%
\usepackage{setspace}
\setstretch{1.5}

@@

This project aims to develop a fully functional software tool capable of accurately predicting a molecule’s inhibition potential (\gls{ic50}), leveraging existing data from the ChEMBL database \cite{ChemblDatabase}. The software is thoroughly documented and available in the GitHub repository: \href{https://github.com/SirSergi0/Repository—AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI Application for Azophotoswitches Optimization with Pharmacological Interest}} \cite{GitHub}.

@@

\newpage
\section{Methodology}\label{sectionMethodology}
The source code is entirely stored in the \href{https://github.com/SirSergi0/Repository---AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI application for azophotoswitches optimization with pharmacological interest} GitHub repository}\cite{GitHub} and it has been entirely written by Sergio Castañeiras Morales for this project. The consultace of this repository is highly recommended in order to comprehended the insights and the workflow of the project. By the time this project is presented, it remains as an open-source repository of the MolBioMed research group \cite{molbiomed}.

@@

\begin{table}[H]
    \centering	
	\caption{Conditions and statistics for the machine's learning models in the computation of the \gls{ic50} from Tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}).}
	\label{TableStatisitcsMainResults}
	\begin{tabular}{c|c}
		Mean Squared Error       & 1202.70\\\hline
		$r^2$ 	                 & 0.90\\\hline
		True Positive            & 994\\\hline
		False Positive           & 8\\\hline
		True Negative            & 1015\\\hline
		False Negative           & 101\\\hline
		True Positive Rate       & 0.90\\\hline
		True Negative Rate       & 0.99\\\hline
		ClassificationAcuracy    & 0.95\\\hline
		MatthewsCorrelationFactor& 0.90
    \end{tabular}
\end{table}
At this stage, it is important to note that the model is currently unable to distinguish between the active and inactive conformations of a molecule, i.e, between the \emph{cis} and \emph{trans} isomers. This limitation is not due to the model architecture or the way chemical descriptors are computed, but rather to a deficiency in the training data. The ChEMBL database \cite{ChemblDatabase} does not explicitly include \emph{cis}/\emph{trans} comparable molecular configurations. In other words, if cis/trans isomerization appears we can only find one of the two conformations in the database, typically the one with higher inhibition potential. Consequently, the model cannot learn to differentiate them since this distinction is not encoded in the dataset. As a result, the model provides \gls{ic50} predictions corresponding to the conformation it has implicitly learned, the more active configuration, which in our context is the \emph{cis} form.

@@

\begin{table}[H]
\centering
\caption{Table of potential photoswitches derivated from Celecoxib's azo-derivates with pyrazole as heterocycle}
\label{tableCelecoxibPyrazole}
\begin{tabular}{c||c|c|c}
Identifier & \ch{R_1} & \ch{R_2} & \ch{R_3} \\\hline\hline
\ref{figureCelecoxibPyrazole}.1 & \ch{CF_3} & \ch{CH_2CH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.2 & \ch{CF_3} & \ch{CH_2CH_3}  & \ch{F}\\\hline
\ref{figureCelecoxibPyrazole}.3 & \ch{CF_3} & \ch{CH_3}  & \ch{F}\\\hline
\ref{figureCelecoxibPyrazole}.4 & \ch{CF_3} & \ch{OCH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.5 & \ch{CF_3} & \ch{OCH_3}  & \ch{F}\\\hline
\ref{figureCelecoxibPyrazole}.6 & \ch{CF_3} & \ch{CH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.7 & \ch{H} & \ch{CH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.8 & \ch{F} & \ch{CH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.9 & \ch{Cl} & \ch{CH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.10 & \ch{Br} & \ch{CH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.11 & \ch{CH_3} & \ch{CH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.12 & \ch{H} & \ch{CH_3}  & \ch{F}\\\hline
\ref{figureCelecoxibPyrazole}.13 & \ch{F} & \ch{CH_3}  & \ch{F}\\\hline
\ref{figureCelecoxibPyrazole}.14 & \ch{Cl} & \ch{CH_3}  & \ch{F}\\\hline
\ref{figureCelecoxibPyrazole}.15 & \ch{Br} & \ch{CH_3}  & \ch{F}\\\hline
\ref{figureCelecoxibPyrazole}.16 & \ch{CH_3} & \ch{CH_3}  & \ch{F}
\end{tabular}
\end{table}
%\begin{figure}[H]
%\captionsetup{type=scheme}
%\centering
%\scalebox{0.8}{
%\chemname{\chemfig[angle increment=30]{
%H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-CF_3)-(-[:45]N=[3]N-[:135]*6(-=-(--[3])=N-=))=-))=-=)
%}}{Pyridine derivative}}
%\par
%\vspace{0.5cm}
%\scalebox{0.8}{
%\chemname{\chemfig[angle increment=30]{
%H_3C-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-CF_3)-(-[:45]N=[3]N-[:135]*6(-=-(-)=N-=))=-))=-=)
%}}{\ch{SO_2CH_3} group derivative}}
%\caption{Scheme for Celecoxib azo-derivatives based on pyridine and \ch{SO_2CH_3} groups.}
%\label{tableCelecoxibPyridine}
%\end{figure}

@@

\begin{table}[H]
\centering
\caption{Table of potential photoswitches derivated from Celecoxib's azo-derivates with furan as heterocycle.}
\label{tableCelecoxibFuran}
\begin{tabular}{c||c|c}
Identifier & \ch{R_1} & \ch{R_2} \\\hline\hline
\ref{figureCelecoxibFuran}.1 & \ch{CF_3} & \ch{H} \\\hline
\ref{figureCelecoxibFuran}.2 & \ch{H} & \ch{H} \\\hline
\ref{figureCelecoxibFuran}.3 & \ch{F} & \ch{H} \\\hline
\ref{figureCelecoxibFuran}.4 & \ch{Cl} & \ch{H} \\\hline
\ref{figureCelecoxibFuran}.5 & \ch{Br} & \ch{H} \\\hline
\ref{figureCelecoxibFuran}.6 & \ch{CH_3} & \ch{H} \\\hline
\ref{figureCelecoxibFuran}.7 & \ch{CF_3} & \ch{F} \\\hline
\ref{figureCelecoxibFuran}.8 & \ch{H} & \ch{F} \\\hline
\ref{figureCelecoxibFuran}.9 & \ch{F} & \ch{F} \\\hline
\ref{figureCelecoxibFuran}.10 & \ch{Cl} & \ch{F} \\\hline
\ref{figureCelecoxibFuran}.11 & \ch{Br} & \ch{F} \\\hline
\ref{figureCelecoxibFuran}.12 & \ch{CH_3} & \ch{F}
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Table of potential photoswitches derivated from Celecoxib's azo-derivates with thiophene as heterocycle.}
\label{tableCelecoxibThiophene}
\begin{tabular}{c||c|c}
Identifier & \ch{R_1} & \ch{R_2} \\\hline\hline
\ref{figureCelecoxibThiophene}.1 & \ch{F} & \ch{H} \\\hline
\ref{figureCelecoxibThiophene}.2 & \ch{H} & \ch{F} \\\hline
\ref{figureCelecoxibThiophene}.3 & \ch{Cl} & \ch{F} 
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Table of potential photoswitches derivated from Celecoxib's azo-derivates with pyrrole as heterocycle.}
\label{tableCelecoxibPyrrole}
\begin{tabular}{c||c|c|c}
Identifier & \ch{R_1} & \ch{R_2} & \ch{R_3} \\\hline\hline
\ref{figureCelecoxibPyrrole}.1 & \ch{CF_3} & \ch{CH_3} & \ch{H} \\\hline
\ref{figureCelecoxibPyrrole}.2 & \ch{Cl} & \ch{CH_3} & \ch{F} 
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Table of potential photoswitches derivated from Celecoxib azo-derivatives with benzene in place of the original heterocycle.}
\label{tableCelecoxibBenzene}
\begin{tabular}{c||c|c}
Identifier & \ch{R_1} & \ch{R_2} \\\hline\hline
\ref{figureCelecoxibBenzene}.1 & \ch{CF_3} & \ch{CH_2CH_3} \\\hline
\ref{figureCelecoxibBenzene}.2 & \ch{CF_3} & \ch{NCH_3COCH_3} \\\hline
\ref{figureCelecoxibBenzene}.3 & \ch{CF_3} & \ch{NHCH_3} \\\hline
\ref{figureCelecoxibBenzene}.4 & \ch{CF_3} & \ch{OCH_3} \\\hline
\ref{figureCelecoxibBenzene}.5 & \ch{Cl} & \ch{CH_3} 
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Table of potential photoswitches derivated from Celecoxib azo-derivatives with indole ring as a heterocycle.}
\label{tableCelecoxibIndole}
\begin{tabular}{c||c}
Identifier & \ch{R_1}  \\\hline\hline
\ref{figureCelecoxibIndole}.1 & \ch{H} \\\hline
\ref{figureCelecoxibIndole}.2 & \ch{F} 
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Table of potential photoswitches derivated from Celecoxib azo-derivatives with two rings of five members joint as a heterocycle.}
\label{tableCelecoxibTwoRings}
\begin{tabular}{c||c|c|c}
Identifier & \ch{R_1} & \ch{R_2} & \ch{R_3} \\\hline\hline
\ref{figureCelecoxibTwoRings}.1 & \ch{NH} & \ch{NH} & \ch{H} \\\hline
\ref{figureCelecoxibTwoRings}.2 & \ch{NH} & \ch{O} & \ch{H} \\\hline
\ref{figureCelecoxibTwoRings}.3 & \ch{O} & \ch{NH} & \ch{H} \\\hline
\ref{figureCelecoxibTwoRings}.4 & \ch{O} & \ch{O} & \ch{H} \\\hline
\ref{figureCelecoxibTwoRings}.5 & \ch{NH} & \ch{NH} & \ch{CH_3} \\\hline
\ref{figureCelecoxibTwoRings}.6 & \ch{NH} & \ch{O} & \ch{CH_3} \\\hline
\ref{figureCelecoxibTwoRings}.7 & \ch{O} & \ch{NH} & \ch{CH_3} \\\hline
\ref{figureCelecoxibTwoRings}.8 & \ch{O} & \ch{O} & \ch{CH_3}
\end{tabular}
\end{table}

\section{Tables of results}\label{appendixTableOfResults}

@@

\begin{table}[H]
    \centering
	\caption{Results for the $\Delta$G$_{binding}$ and \gls{ic50}. The conditions and estatistics under which this computations have been done are stored in Table (\ref{TableConditionsMainResults}).}
	\label{TableMainResults1}
	\begin{tabular}{c|c|c|c|c|c|c}
		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ (Kcal/mol) & Predicted \gls{ic50} (nM) \\ \hline\hline
		Pyrazole & \ref{figureCelecoxibPyrazole}.1 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{H} & -4.3505 & 145 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.2 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{F} & -3.619 & 160 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.3 & \ch{CF_3} & \ch{CH_3} & \ch{F} & -0.5452 & 192 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.4 & \ch{CF_3} & O\ch{CH_3} & \ch{H} & 9.9793 & 306 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.5 & \ch{CF_3} & O\ch{CH_3} & \ch{F} & 1.5591 & 238 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.6 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -5.3292 & 142 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.8 & \ch{F} & \ch{CH_3} & \ch{H} & 5.0694 & 240 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.9 & \ch{Cl} & \ch{CH_3} & \ch{H} & -1.1579 & 171 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.10 & \ch{Br} & \ch{CH_3} & \ch{H} & 6.3225 & 247 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.11 & \ch{CH_3} & \ch{CH_3} & \ch{H} & 3.0677 & 215 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.12 & \ch{H} & \ch{CH_3} & \ch{F} & 1.0334 & 196 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.13 & \ch{F} & \ch{CH_3} & \ch{F} & 3.2216 & 220 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.14 & \ch{Cl} & \ch{CH_3} & \ch{F} & 5.1623 & 231 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.15 & \ch{Br} & \ch{CH_3} & \ch{F} & 5.6163 & 235 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.16 & \ch{CH_3} & \ch{CH_3} & \ch{F} & -3.3079 & 149 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.1 & \ch{CF_3} & \ch{H} &  & -0.9611 & 171 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.2 & \ch{H} & \ch{H} &  & 0.193 & 189 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.3 & \ch{F} & \ch{H} &  & -4.8383 & 133 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.4 & \ch{Cl} & \ch{H} &  & -2.4267 & 158 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.5 & \ch{Br} & \ch{H} &  & -3.4217 & 144 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.6 & \ch{CH_3} & \ch{H} &  & -3.9711 & 139 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.7 & \ch{CF_3} & \ch{F} &  & -5.4022 & 148 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.8 & \ch{H} & \ch{F} &  & -6.55 & 122 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.9 & \ch{F} & F &  & -0.1311 & 189\\ \hline
        Furan & \ref{figureCelecoxibFuran}.10 & \ch{Cl} & \ch{F} &  & -5.8185 & 127\\ \hline
        Furan & \ref{figureCelecoxibFuran}.11 & \ch{Br} & \ch{F} &  & 6.1474 & 241
            \end{tabular}
\end{table}

>>>>

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
%----------FONT AND GEOMETRY DEFINITION----------%
\usepackage[a4paper, top=3.0cm, bottom=3.0cm, left = 3.0cm, right = 3.0cm]{geometry}
\voffset = -0.75cm
\usepackage{arev}
\usepackage{helvet}
\renewcommand{\rmdefault}{\sfdefault}
\usepackage[math]{blindtext}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd, esint}
%---------SPACING----------%
\usepackage{setspace}
\setstretch{1.5}
\usepackage[table]{xcolor}

@@

This project aims to develop a fully functional software tool capable of accurately predicting a molecule’s inhibition potential (\gls{ic50}), leveraging existing data from the ChEMBL database \cite{ChemblDatabase}. The software is thoroughly documented and available in the GitHub repository: \href{https://github.com/SirSergi0/Repository—AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI Application for Azophotoswitches Optimization with Pharmacological Interest}} \cite{GitHub}\cite{azophotoswitches2025}.

@@

\newpage
\section{Methodology}\label{sectionMethodology}
The source code is entirely stored in the \href{https://github.com/SirSergi0/Repository---AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI application for azophotoswitches optimization with pharmacological interest} GitHub repository}\cite{GitHub} and it has been entirely written by Sergio Castañeiras Morales for this project\cite{azophotoswitches2025}. The consultace of this repository is highly recommended in order to comprehended the insights and the workflow of the project. By the time this project is presented, it remains as an open-source repository of the MolBioMed research group \cite{molbiomed}.

@@

%\begin{table}[H]
%    \centering	
%	\caption{Conditions and statistics for the machine's learning models in the computation of the \gls{ic50} from Tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}).}
%	\label{TableStatisitcsMainResults}
%	\begin{tabular}{c|c}
%		Mean Squared Error       & 1202.70\\\hline
%		$r^2$ 	                 & 0.90\\\hline
%		True Positive            & 994\\\hline
%		False Positive           & 8\\\hline
%		True Negative            & 1015\\\hline
%		False Negative           & 101\\\hline
%		True Positive Rate       & 0.90\\\hline
%		True Negative Rate       & 0.99\\\hline
%		ClassificationAcuracy    & 0.95\\\hline
%		MatthewsCorrelationFactor& 0.90
%    \end{tabular}
%\end{table}

\begin{table}[H]
    \centering
    \caption{Conditions and statistics for the machine's learning models in the computation of the \gls{ic50} from Tables~\ref{TableMainResults1} and~\ref{TableMainResults2}.}
    \label{TableStatisitcsMainResults}
    \setlength{\tabcolsep}{12pt}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{|>{\columncolor{gray!20}}c||c|}
        \hline
        \rowcolor{gray!20}
        \textbf{Metric} & \textbf{Value} \\
        \hline\hline
        Mean Squared Error        & 1202.70 \\
        $r^2$                     & 0.90 \\
        True Positive             & 994 \\
        False Positive            & 8 \\
        True Negative             & 1015 \\
        False Negative            & 101 \\
        True Positive Rate        & 0.90 \\
        True Negative Rate        & 0.99 \\
        Classification Accuracy   & 0.95 \\
        Matthews Correlation Coefficient & 0.90 \\
        \hline
    \end{tabular}
\end{table}

At this stage, it is important to note that the model is currently unable to distinguish between the active and inactive conformations of a molecule, i.e, between the \emph{cis} and \emph{trans} isomers. This limitation is not due to the model architecture or the way chemical descriptors are computed, but rather to a deficiency in the training data. The ChEMBL database \cite{ChemblDatabase} does not explicitly include \emph{cis}/\emph{trans} comparable molecular configurations. In other words, if cis/trans isomerization appears we can only find one of the two conformations in the database, typically the one with higher inhibition potential. Consequently, the model cannot learn to differentiate them since this distinction is not encoded in the dataset. As a result, the model provides \gls{ic50} predictions corresponding to the conformation it has implicitly learned, the more active configuration, which in our context is the \emph{cis} form.

@@

\begin{table}[H]
\centering
\caption{Table of potential photoswitches derivated from Celecoxib's azo-derivates with pyrazole as heterocycle}
\label{tableCelecoxibPyrazole}
\begin{tabular}{|>{\columncolor{gray!20}}c||c|c|c|}
        \hline
        \rowcolor{gray!20}
Identifier & \ch{R_1} & \ch{R_2} & \ch{R_3} \\\hline\hline
\ref{figureCelecoxibPyrazole}.1 & \ch{CF_3} & \ch{CH_2CH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.2 & \ch{CF_3} & \ch{CH_2CH_3}  & \ch{F}\\\hline
\ref{figureCelecoxibPyrazole}.3 & \ch{CF_3} & \ch{CH_3}  & \ch{F}\\\hline
\ref{figureCelecoxibPyrazole}.4 & \ch{CF_3} & \ch{OCH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.5 & \ch{CF_3} & \ch{OCH_3}  & \ch{F}\\\hline
\ref{figureCelecoxibPyrazole}.6 & \ch{CF_3} & \ch{CH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.7 & \ch{H} & \ch{CH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.8 & \ch{F} & \ch{CH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.9 & \ch{Cl} & \ch{CH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.10 & \ch{Br} & \ch{CH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.11 & \ch{CH_3} & \ch{CH_3}  & \ch{H}\\\hline
\ref{figureCelecoxibPyrazole}.12 & \ch{H} & \ch{CH_3}  & \ch{F}\\\hline
\ref{figureCelecoxibPyrazole}.13 & \ch{F} & \ch{CH_3}  & \ch{F}\\\hline
\ref{figureCelecoxibPyrazole}.14 & \ch{Cl} & \ch{CH_3}  & \ch{F}\\\hline
\ref{figureCelecoxibPyrazole}.15 & \ch{Br} & \ch{CH_3}  & \ch{F}\\\hline
\ref{figureCelecoxibPyrazole}.16 & \ch{CH_3} & \ch{CH_3}  & \ch{F}\\\hline
\end{tabular}
\end{table}
%\begin{figure}[H]
%\captionsetup{type=scheme}
%\centering
%\scalebox{0.8}{
%\chemname{\chemfig[angle increment=30]{
%H_2N-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-CF_3)-(-[:45]N=[3]N-[:135]*6(-=-(--[3])=N-=))=-))=-=)
%}}{Pyridine derivative}}
%\par
%\vspace{0.5cm}
%\scalebox{0.8}{
%\chemname{\chemfig[angle increment=30]{
%H_3C-S(=[3]O)(=[9]O)-*6(-=-(-N*5(-N=(-CF_3)-(-[:45]N=[3]N-[:135]*6(-=-(-)=N-=))=-))=-=)
%}}{\ch{SO_2CH_3} group derivative}}
%\caption{Scheme for Celecoxib azo-derivatives based on pyridine and \ch{SO_2CH_3} groups.}
%\label{tableCelecoxibPyridine}
%\end{figure}

@@

\begin{table}[H]
\centering
\caption{Table of potential photoswitches derivated from Celecoxib's azo-derivates with furan as heterocycle.}
\label{tableCelecoxibFuran}
\begin{tabular}{|>{\columncolor{gray!20}}c||c|c|}
\hline
\rowcolor{gray!20}
Identifier & \ch{R_1} & \ch{R_2} \\\hline\hline
\ref{figureCelecoxibFuran}.1 & \ch{CF_3} & \ch{H} \\\hline
\ref{figureCelecoxibFuran}.2 & \ch{H} & \ch{H} \\\hline
\ref{figureCelecoxibFuran}.3 & \ch{F} & \ch{H} \\\hline
\ref{figureCelecoxibFuran}.4 & \ch{Cl} & \ch{H} \\\hline
\ref{figureCelecoxibFuran}.5 & \ch{Br} & \ch{H} \\\hline
\ref{figureCelecoxibFuran}.6 & \ch{CH_3} & \ch{H} \\\hline
\ref{figureCelecoxibFuran}.7 & \ch{CF_3} & \ch{F} \\\hline
\ref{figureCelecoxibFuran}.8 & \ch{H} & \ch{F} \\\hline
\ref{figureCelecoxibFuran}.9 & \ch{F} & \ch{F} \\\hline
\ref{figureCelecoxibFuran}.10 & \ch{Cl} & \ch{F} \\\hline
\ref{figureCelecoxibFuran}.11 & \ch{Br} & \ch{F} \\\hline
\ref{figureCelecoxibFuran}.12 & \ch{CH_3} & \ch{F}\\\hline
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Table of potential photoswitches derivated from Celecoxib's azo-derivates with thiophene as heterocycle.}
\label{tableCelecoxibThiophene}
\begin{tabular}{|>{\columncolor{gray!20}}c||c|c|}
\hline
\rowcolor{gray!20}
Identifier & \ch{R_1} & \ch{R_2} \\\hline\hline
\ref{figureCelecoxibThiophene}.1 & \ch{F} & \ch{H} \\\hline
\ref{figureCelecoxibThiophene}.2 & \ch{H} & \ch{F} \\\hline
\ref{figureCelecoxibThiophene}.3 & \ch{Cl} & \ch{F} \\\hline
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Table of potential photoswitches derivated from Celecoxib's azo-derivates with pyrrole as heterocycle.}
\label{tableCelecoxibPyrrole}
\begin{tabular}{|>{\columncolor{gray!20}}c||c|c|c|}
\hline
\rowcolor{gray!20}
Identifier & \ch{R_1} & \ch{R_2} & \ch{R_3} \\\hline\hline
\ref{figureCelecoxibPyrrole}.1 & \ch{CF_3} & \ch{CH_3} & \ch{H} \\\hline
\ref{figureCelecoxibPyrrole}.2 & \ch{Cl} & \ch{CH_3} & \ch{F} \\\hline
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Table of potential photoswitches derivated from Celecoxib azo-derivatives with benzene in place of the original heterocycle.}
\label{tableCelecoxibBenzene}
\begin{tabular}{|>{\columncolor{gray!20}}c||c|c|}
\hline
\rowcolor{gray!20}
Identifier & \ch{R_1} & \ch{R_2} \\\hline\hline
\ref{figureCelecoxibBenzene}.1 & \ch{CF_3} & \ch{CH_2CH_3} \\\hline
\ref{figureCelecoxibBenzene}.2 & \ch{CF_3} & \ch{NCH_3COCH_3} \\\hline
\ref{figureCelecoxibBenzene}.3 & \ch{CF_3} & \ch{NHCH_3} \\\hline
\ref{figureCelecoxibBenzene}.4 & \ch{CF_3} & \ch{OCH_3} \\\hline
\ref{figureCelecoxibBenzene}.5 & \ch{Cl} & \ch{CH_3} \\\hline
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Table of potential photoswitches derivated from Celecoxib azo-derivatives with indole ring as a heterocycle.}
\label{tableCelecoxibIndole}
\begin{tabular}{|>{\columncolor{gray!20}}c||c|}
\hline
\rowcolor{gray!20}
Identifier & \ch{R_1}  \\\hline\hline
\ref{figureCelecoxibIndole}.1 & \ch{H} \\\hline
\ref{figureCelecoxibIndole}.2 & \ch{F} \\\hline
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Table of potential photoswitches derivated from Celecoxib azo-derivatives with two rings of five members joint as a heterocycle.}
\label{tableCelecoxibTwoRings}
\begin{tabular}{|>{\columncolor{gray!20}}c||c|c|c|}
\hline
\rowcolor{gray!20}
Identifier & \ch{R_1} & \ch{R_2} & \ch{R_3} \\\hline\hline
\ref{figureCelecoxibTwoRings}.1 & \ch{NH} & \ch{NH} & \ch{H} \\\hline
\ref{figureCelecoxibTwoRings}.2 & \ch{NH} & \ch{O} & \ch{H} \\\hline
\ref{figureCelecoxibTwoRings}.3 & \ch{O} & \ch{NH} & \ch{H} \\\hline
\ref{figureCelecoxibTwoRings}.4 & \ch{O} & \ch{O} & \ch{H} \\\hline
\ref{figureCelecoxibTwoRings}.5 & \ch{NH} & \ch{NH} & \ch{CH_3} \\\hline
\ref{figureCelecoxibTwoRings}.6 & \ch{NH} & \ch{O} & \ch{CH_3} \\\hline
\ref{figureCelecoxibTwoRings}.7 & \ch{O} & \ch{NH} & \ch{CH_3} \\\hline
\ref{figureCelecoxibTwoRings}.8 & \ch{O} & \ch{O} & \ch{CH_3}\\\hline
\end{tabular}
\end{table}

\newpage
\section{Tables of results}\label{appendixTableOfResults}

@@

\begin{table}[H]
    \centering
	\caption{Results for the $\Delta$G$_{binding}$ and \gls{ic50}. The conditions and estatistics under which this computations have been done are stored in Table (\ref{TableConditionsMainResults}).}
	\label{TableMainResults1}
	\begin{tabular}{|>{\columncolor{gray!20}}c|c|c|c|c|c|c|}
	\hline
\rowcolor{gray!20}
		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ (Kcal/mol) & Predicted \gls{ic50} (nM) \\ \hline\hline
		Pyrazole & \ref{figureCelecoxibPyrazole}.1 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{H} & -4.3505 & 145 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.2 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{F} & -3.619 & 160 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.3 & \ch{CF_3} & \ch{CH_3} & \ch{F} & -0.5452 & 192 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.4 & \ch{CF_3} & O\ch{CH_3} & \ch{H} & 9.9793 & 306 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.5 & \ch{CF_3} & O\ch{CH_3} & \ch{F} & 1.5591 & 238 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.6 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -5.3292 & 142 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.8 & \ch{F} & \ch{CH_3} & \ch{H} & 5.0694 & 240 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.9 & \ch{Cl} & \ch{CH_3} & \ch{H} & -1.1579 & 171 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.10 & \ch{Br} & \ch{CH_3} & \ch{H} & 6.3225 & 247 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.11 & \ch{CH_3} & \ch{CH_3} & \ch{H} & 3.0677 & 215 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.12 & \ch{H} & \ch{CH_3} & \ch{F} & 1.0334 & 196 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.13 & \ch{F} & \ch{CH_3} & \ch{F} & 3.2216 & 220 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.14 & \ch{Cl} & \ch{CH_3} & \ch{F} & 5.1623 & 231 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.15 & \ch{Br} & \ch{CH_3} & \ch{F} & 5.6163 & 235 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.16 & \ch{CH_3} & \ch{CH_3} & \ch{F} & -3.3079 & 149 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.1 & \ch{CF_3} & \ch{H} &  & -0.9611 & 171 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.2 & \ch{H} & \ch{H} &  & 0.193 & 189 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.3 & \ch{F} & \ch{H} &  & -4.8383 & 133 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.4 & \ch{Cl} & \ch{H} &  & -2.4267 & 158 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.5 & \ch{Br} & \ch{H} &  & -3.4217 & 144 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.6 & \ch{CH_3} & \ch{H} &  & -3.9711 & 139 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.7 & \ch{CF_3} & \ch{F} &  & -5.4022 & 148 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.8 & \ch{H} & \ch{F} &  & -6.55 & 122 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.9 & \ch{F} & F &  & -0.1311 & 189\\ \hline
        Furan & \ref{figureCelecoxibFuran}.10 & \ch{Cl} & \ch{F} &  & -5.8185 & 127\\ \hline
        Furan & \ref{figureCelecoxibFuran}.11 & \ch{Br} & \ch{F} &  & 6.1474 & 241\\ \hline
            \end{tabular}
\end{table}
